The Concurrent Calculi Formalisation Benchmark

### 2024-04-17 short-paper/short-paper.tex
Remove appendix for camera ready version.
Change variant spelling to more common.

Our benchmark challenges (detailed in \cref{app:challenges} and on our website) consider
\emph{in isolation} three key aspects that frequently pose difficulties
when mechanising concurrency theory, which we will discuss in more detail in the next section: \emph{linearity}, \emph{scope
  extrusion}, and \emph{coinductive reasoning}.
Mechanisations must often address several of these aspects at the same time; however, we
see the combination of techniques as a next
step, as discussed in \cref{sec:going-beyond}.

@@

\subsection{Scope Extrusion}
This challenge revolves around the mechanisation of scope
extrusion, by which a process can send restricted names to another
process, as long as the restriction can safely be extruded to include
the receiving process.  The setting for this challenge is a
``classic'' untyped \( \pi \)-calculus, where (unlike the calculi in
the other challenges) names can be sent and received, and bound by
input constructs.  We define two different semantics for our system:
\begin{enumerate}
\item A reduction system: this avoids explicit reasoning about scope
  extrusion by using structural congruence, allowing
  implementors to explore different ways to encode the latter (\eg
  via process contexts or compatible refinement);
\item An (early) labelled transition system.
\end{enumerate}
The goal of our challenge on scope extrusion is to prove that the two semantics are
equivalent up to structural congruence.

@@

\clearpage
\appendix
\section{Challenges}\label{app:challenges}
\input{../challenges/challenges.tex}

>>>>

Our benchmark challenges (detailed on our website linked below) consider
\emph{in isolation} three key aspects that frequently pose difficulties
when mechanising concurrency theory, which we will discuss in more detail in the next section: \emph{linearity}, \emph{scope
  extrusion}, and \emph{coinductive reasoning}.
Mechanisations must often address several of these aspects at the same time; however, we
see the combination of techniques as a next
step, as discussed in \cref{sec:going-beyond}.

@@

\subsection{Scope Extrusion}
This challenge revolves around the mechanisation of scope
extrusion, by which a process can send restricted names to another
process, as long as the restriction can safely be extruded to include
the receiving process.  The setting for this challenge is a
``classic'' untyped \( \pi \)-calculus, where (unlike the calculi in
the other challenges) names can be sent and received, and bound by
input constructs.  We define two different semantics for our system:
\begin{enumerate}
\item A reduction system: this avoids explicit reasoning about scope
  extrusion by using structural congruence, allowing
  implementers to explore different ways to encode the latter (\eg
  via process contexts or compatible refinement);
\item An (early) labelled transition system.
\end{enumerate}
The goal of our challenge on scope extrusion is to prove that the two semantics are
equivalent up to structural congruence.

@@
